---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hordes

<!-- badges: start -->
<!-- badges: end -->

The goal of hordes is to provide data translation functions for the `hordes` NodeJS package.

## Installation

``` r
# install.packages("remotes")
remotes::install_github("colinfay/hordes", subdir = "r-hordes")

```
## Example

The `{hordes}` R package simplifies data translation from R to NodeJS. 

For example, to share images, you can create a function in a package (here named "`{hordex}`") that does: 

```{r}
ggpoint <- function(n) {
  gg <- ggplot(iris[1:n, ], aes(Sepal.Length, Sepal.Width)) +
    geom_point()
  hordes::base64_img_ggplot(gg)
}
```

Then in NodeJS:

```javascript
const express = require('express');
const {library} = require('hordes');
const app = express();
const hordesx = library("hordesx")

app.get('/ggplot', async (req, res) => {
    try {
        const im = await hordesx.ggpoint(`n = ${req.query.n}`);
        const img = Buffer.from(im, 'base64');
        res.writeHead(200, {
          'Content-Type': 'image/png',
          'Content-Length': img.length
        });
      res.end(img); 
    } catch(e){
        res.status(500).send(e)
    }
})

app.listen(2811, function () {
  console.log('Example app listening on port 2811!')
})
```

> http://localhost:2811/ggplot?n=5

> http://localhost:2811/ggplot?n=50

> http://localhost:2811/ggplot?n=150

## Code of Conduct

Please note that the hordes project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
