# Data Exchange 

If you want to exchange data between R and NodeJS, use an interchangeable format (JSON, arrow, base64 for images, raw strings...).

## The `hordes` R package

There is a `hordes` R package that contains some functions to facilitate the data translation. 

It can be installed with 

```r
remotes::install_github("colinfay/hordes", subdir = "r-hordes")
```

## JSON

Return

```javascript
const {library} = require('hordes');
const jsonlite = library("jsonlite");
const base = library("base");

(async () => {
    try {
            const a = await jsonlite.toJSON("iris")
            console.log(JSON.parse(a)[0])
        } catch(e){
            console.log(e)
        }
}
)();
```

```
{
  'Sepal.Length': 5.1,
  'Sepal.Width': 3.5,
  'Petal.Length': 1.4,
  'Petal.Width': 0.2,
  Species: 'setosa'
}
```

## Text

By default, everything is returned as an array of string. 
From the R side, it's better to print things with `cat`, as it allows to avoid the `[1] ` in front of the console printing. 

```{r}
21
```


```javascript
(async () => {
    try {
            const b = await base.cat("21")
            console.log(parseInt(b) * 2)
        } catch(e){
            console.log(e)
        }
}
)();
```

## Base64 images

Given the following R function, contained in a package called `{hordesx}`

```{r}
ggpoint <- function(n) {
  gg <- ggplot(iris[1:n, ], aes(Sepal.Length, Sepal.Width)) +
    geom_point()
  hordes::base64_img_ggplot(gg)
}

```


```javascript
const express = require('express');
const {library} = require('hordes');
const app = express();
const hordesx = library("hordesx")

app.get('/ggplot', async (req, res) => {
    try {
        const im = await hordesx.ggpoint(`n = ${req.query.n}`);
        const img = Buffer.from(im, 'base64');
        res.writeHead(200, {
          'Content-Type': 'image/png',
          'Content-Length': img.length
        });
      res.end(img); 
    } catch(e){
        res.status(500).send(e)
    }
})

app.listen(2811, function () {
  console.log('Example app listening on port 2811!')
})
```

> http://localhost:2811/ggplot?n=5

> http://localhost:2811/ggplot?n=50

> http://localhost:2811/ggplot?n=150

## Files & Paths

// TODO 

## Arrow 

// TODO 

## Stream

// TODO
